---
title: "Hyewon project"
author: "Ebby Raymundo"
date: "3/22/2021"
output: pdf_document
---

# Description
This file takes Qualtrics data from phase 1 of the friendship survey and checks the data for anyone that has signed up twice, demographics portions that have been done twice, more than 1 person selecting the same friend, and unfinished demographic surveys. Sometimes people misspell their friend's name or one uses a nickname when signing up which can be accounted for by checking the outputs from this script.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(smodels)
library(lubridate)
```

Slicing out Qualtrics metadata.
```{r}
enrollment <- read.csv("data/Consent and Enrollment.csv", header = TRUE) %>%
              slice(-2)

demographics <- read.csv("data/Demographics.csv", header = TRUE) %>%
                slice(-2)
```

# People that signed up twice (finished)

```{r}
self_enrolled_twice <- enrollment %>%
  slice(-1) %>%
  mutate(
    self_1 = str_trim(str_to_lower(self_1)),
    self_8 = str_trim(str_to_lower(self_8)),
    friend_1 = str_trim(str_to_lower(friend_1)),
    friend_2 = str_trim(str_to_lower(friend_2))
    ) %>%
  group_by(self_1) %>%
  mutate(name = sm_count(self_1)) %>%
  group_by(self_8) %>%
  mutate(email = sm_count(self_8)) %>%
  filter(name != 1 | email != 1) %>%
  select(self_1, self_8, friend_1, friend_2, name, email, subjectid)
```

# Demographics that have been done twice (finished)

```{r}
demographics_done_twice <- enrollment %>%
  slice(-1) %>%
  left_join(y = demographics[,c("Finished", "subjectid")], by = "subjectid") %>%
  group_by(self_8) %>%
  mutate(sm_count()) %>%
  select(self_1, self_8, subjectid, count) %>%
  filter(count != 1)
```


# Same friend is enrolled twice (finished)

```{r}
friend_enrolled_twice <- enrollment %>%
  slice(-1) %>%
  filter(friend_registered != "N/A (I am registering alone)") %>%
  transmute(
    self_1 = str_trim(str_to_lower(self_1)),
    self_8 = str_trim(str_to_lower(self_8)),
    friend_1 = str_trim(str_to_lower(friend_1)),
    friend_2 = str_trim(str_to_lower(friend_2))
    ) %>%
  group_by(friend_1) %>%
  mutate(name = sm_count(friend_1)) %>%
  group_by(friend_2) %>%
  mutate(email = sm_count(friend_2)) %>%
  filter(name != 1 | email != 1)
```

# Showing anyone that hasn't finished the demographic survey (Finished)
Just need name, email, and subject ID (for demographic URL survey)

```{r}
unfinished_demographics <- enrollment %>%
  left_join(y = demographics[,c("Finished", "subjectid")], by = "subjectid") %>%
  filter(is.na(Finished.y)) %>% # filtering on NAs doesn't work if you just do Finished.y == NA or "NA"
  select(self_1, self_8, subjectid, Finished.y) # participant's own name and email
```

# Show people that have nominated someone but friend hasn't registered yet (Finished)
Names and emails of both parties, mark the one that isn't registered. Mark how long it's been since they've nominated their friend

```{r}
currentDate = Sys.Date()

friend_isnt_enrolled <- enrollment %>%
  slice(-1) %>%
  filter(friend_registered != "N/A (I am registering alone)") %>%
  mutate(
    self_1 = str_trim(str_to_lower(self_1)),
    self_8 = str_trim(str_to_lower(self_8)),
    friend_1 = str_trim(str_to_lower(friend_1)),
    friend_2 = str_trim(str_to_lower(friend_2))
    ) %>%
  mutate(friend_enrolled = FALSE) %>%
  mutate(friend_enrolled = if_else(friend_1 %in% self_1, TRUE, friend_enrolled)) %>%
  mutate(friend_enrolled = if_else(friend_2 %in% self_8, TRUE, friend_enrolled)) %>%
  mutate(EndDate = mdy_hm(EndDate)) %>%
  mutate(days_since = difftime(currentDate, EndDate, units = "days")) %>%
  filter(friend_enrolled == FALSE) %>%
  select(EndDate, self_1, self_8, friend_1, friend_2, days_since, friend_registered, friend_prior_action, subjectid) %>%
  arrange(desc(days_since))
```

# Reassigns people with unregistered friends, generates dyad IDs (run after friend_isnt_enrolled)

```{r}
set.seed(1)
DID <- vector(length = 999) # resets/creates vector that contains used vs unused DIDs
friendNames <- vector(length = 999)
# Creates new DID that checks DID vector to see if randint chosen has already been used
newDID <- function() {
  
  randint <- floor(runif(1, min = 100, max = 1000)) # actual max is 999 since it'll never equal 1000
  
  while(DID[randint] == TRUE) { # has already been used, try again
    randint <- floor(runif(1, min = 100, max = 1000))
  }
  DID[randint] <<- TRUE
  return(randint)
}

friend_ID <- function(ownName, friendName) {
  index1 <- which(friendNames == ownName) # check if self has been seen yet
  index2 <- which(friendNames == friendName)
  
  if (length(index1) == 0 & length(index2) == 0) { # friend not found yet, need new ID
    createdDID <- newDID()
    friendNames[createdDID] <<- ownName # neither name seen, put self in
    return(createdDID)
  }
  return(index2) # either one of names seen, friend has been seen before
}

reassigned_enrollment <- enrollment %>%
    mutate(
    self_1 = str_trim(str_to_lower(self_1)),
    self_8 = str_trim(str_to_lower(self_8)),
    friend_1 = str_trim(str_to_lower(friend_1)),
    friend_2 = str_trim(str_to_lower(friend_2))
    ) %>%
  mutate(friend_1 = ifelse(self_1 %in% friend_isnt_enrolled$self_1, "", friend_1)) %>%
  mutate(friend_2 = ifelse(self_1 %in% friend_isnt_enrolled$self_1, "", friend_2)) %>%
  mutate(friend_registered = ifelse(self_1 %in% friend_isnt_enrolled$self_1, "N/A (I am registering alone)", friend_registered)) %>%
  mutate(friend_prior_action = ifelse(self_1 %in% friend_isnt_enrolled$self_1, "", friend_prior_action))

dyad_ID <- reassigned_enrollment %>%
  slice(-1) %>%
  mutate(dyadid = NA) %>%
  rowwise() %>%
  mutate(dyadid = ifelse(friend_registered != "N/A (I am registering alone)", friend_ID(self_8, friend_2), dyadid)) %>%
  arrange(dyadid)

```

# Master key (run after reassigned enrollment)

```{r}
master_key <- dyad_ID %>%
  left_join(y = demographics[,c("Finished", "subjectid")], by = "subjectid") %>%
  mutate(paired = ifelse(friend_registered != "N/A (I am registering alone)", TRUE, FALSE)) %>%
  rename(name = self_1) %>%
  rename(email = self_8) %>%
  rename(finished_enrollment = Finished.x) %>%
  rename(finished_demographics = Finished.y) %>%
  select(subjectid, dyadid, name, email, finished_enrollment, finished_demographics, paired)
```

Run this if you already have a master key without conditions

```{r}
master_key <- read.csv("data/master_key.csv")
```


# Conditions

```{r}
set.seed(63) # can play around with the seed until you get a percentage split you like. Rerunning the chunk will give consistent results

preassigned_control <- sum(master_key$paired == FALSE)
num_participants <- nrow(master_key)
control_probability <- 0.5 - (preassigned_control / num_participants)
intervention_probability <- 1 - control_probability

# prob: Subtract percentage dedicated to solo participants from control (0.5) for control probability, subtract previous calculation from 1 for remaining probability for intervention condition

master_key <- master_key %>%
  mutate(condition = "control") %>%
  group_by(dyadid) %>%
  mutate(condition = ifelse(
    paired == TRUE,
    sample(
      c("control", "intervention"),
      1,
      replace = TRUE,
      prob = c(control_probability, intervention_probability)
      ),
    condition
    )
  )

sum(master_key$condition == "control") / num_participants # checks percentage of control
```
# Qualtrics links (run after conditions)

```{r}
qualtrics_links <- dyad_ID %>%
  rowwise() %>%
  mutate(link = str_interp("https://richmond.ca1.qualtrics.com/jfe/form/SV_5dOVnvtOliEnQCW?subjectid=${subjectid}&dyad_ID=${dyadid}&paired=${paired}&condition=${condition}&finished_demographics=${finished_demographics}")) %>%
  select(self_8, link)

```

### Sampling methods

```{r}
#Approach: randomly selects from the conditions. May end up slightly off from ideal assignment (e.g. in a pool of 100 ppl, 52 in one group and 48 in the other)
sample(c("control", "intervention"),
       1,
       replace = TRUE,
       prob = c(0.5 - (sum(master_key$paired == FALSE) / nrow(master_key)), 1 - (0.5 - (sum(master_key$paired == FALSE) / nrow(master_key)))))

# Possible second approach: Create a pool of "control" = total participants - solo, and "intervention" = number remaining and randomly pull from that with no replacement
```



# Export

```{r}
write.csv(friend_enrolled_twice, "friend_enrolled_twice.csv", row.names = FALSE)
```
```{r}
write.csv(friend_isnt_enrolled, "friend_isnt_enrolled.csv", row.names = FALSE)
```
```{r}
write.csv(self_enrolled_twice, "self_enrolled_twice.csv", row.names = FALSE)
```
```{r}
write.csv(unfinished_demographics, "unfinished_demographics.csv", row.names = FALSE)
```
```{r}
write.csv(master_key, "data/master_key.csv", row.names = FALSE)
```
```{r}
write.csv(qualtrics_links, "data/qualtrics_links.csv", row.names = FALSE)
```
